### 2018-07-19 modelling.tex
Add conclusion :P

>>>>

\section{Conclusion}

A Bayesian framework for the relative quantification of protein abundance rations (Fold-Change, FC) using \ac{MS1} intensity was presented in this work. Unlike the currently prevailing methods in the field, it provides uncertainty estimates that provide a direct interpretation about the accuracy of the quantification. Moreover, preliminary results on the sequence modelling of the peptide bias revealed that more complex architectures and sequnce features are required to solve this problem. Finally, the method can be used to investigate the presence of batch effects in \ac{MS} experiments for their minimisation in future.
